### 2024-08-09 mythbusters.qmd
20240809 - updates based on updated data object

load(file = "./data/nfl_playerContracts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
load(file = "./data/nfl_espnQBR_seasonal.RData")
```

```{r}
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
load(file = "./data/nfl_espnQBR_seasonal.RData")
```

@@

# Merge with weekly and seasonal stats data
player_stats_weekly_offense <- player_stats_weekly_offense %>% 
  dplyr::mutate(nameMerge = petersenlab::cleanUpNames(player_display_name, ))
#nfl_actualStats_offense_seasonal <- nfl_actualStats_offense_seasonal %>% 
#  mutate(nameMerge = petersenlab::cleanUpNames(player_display_name, ))

@@

player_statsContracts_seasonal$age[which(is.infinite((player_statsContracts_seasonal$age)))] <- NA
player_statsContracts_seasonal$years_of_experience[which(is.infinite((player_statsContracts_seasonal$years_of_experience)))] <- NA

@@

# Merge with QBR data
nfl_espnQBR_seasonal$nameMerge <- paste(nfl_espnQBR_seasonal$name_first, nfl_espnQBR_seasonal$name_last, sep = " ") %>% 
  petersenlab::cleanUpNames(.)

nfl_contractYearQBR_weekly <- nfl_playerContractYears %>% 
  dplyr::filter(position == "QB") %>% 
  dplyr::full_join(
    .,
    nfl_espnQBR_seasonal,
    by = c("nameMerge","team","season")
  )

@@

nfl_contractYearQBRsubset_weekly <- nfl_contractYearQBR_weekly %>% 
  dplyr::filter(
    season_type == "Regular",
    game_week != "Season Total") %>% 
  dplyr::mutate(game_week = as.numeric(game_week)) %>% 
  dplyr::arrange(nameMerge, season, season_type, game_week)

# Merge with age and experience
nfl_contractYearQBRsubset_weekly <- player_statsContractsSubset_offense_weekly %>% 
  dplyr::filter(position == "QB") %>% 
  dplyr::select(nameMerge, season, week, age, years_of_experience) %>% 
  full_join(
    nfl_contractYearQBRsubset_weekly,
    by = c("nameMerge","season", c("week" = "game_week"))
  ) %>% 
  arrange(player_id, season, week)

@@

nfl_contractYearQBR_seasonal$age[which(is.infinite((nfl_contractYearQBR_seasonal$age)))] <- NA
nfl_contractYearQBR_seasonal$years_of_experience[which(is.infinite((nfl_contractYearQBR_seasonal$years_of_experience)))] <- NA

>>>>

load(file = "./data/nfl_playerContracts.RData")
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
load(file = "./data/nfl_espnQBR_seasonal.RData")
load(file = "./data/nfl_espnQBR_weekly.RData")
```

```{r}
load(file = "./data/nfl_playerContracts.RData")
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
load(file = "./data/nfl_espnQBR_seasonal.RData")
load(file = "./data/nfl_espnQBR_weekly.RData")
```

@@

# Merge with weekly and seasonal stats data
player_stats_weekly_offense <- player_stats_weekly_offense %>% 
  dplyr::mutate(nameMerge = petersenlab::cleanUpNames(player_display_name))
#nfl_actualStats_offense_seasonal <- nfl_actualStats_offense_seasonal %>% 
#  mutate(nameMerge = petersenlab::cleanUpNames(player_display_name, ))

@@

player_statsContracts_seasonal[sapply(player_statsContracts_seasonal, is.infinite)] <- NA

@@

# Merge with QBR data
nfl_espnQBR_weekly$nameMerge <- paste(nfl_espnQBR_weekly$name_first, nfl_espnQBR_weekly$name_last, sep = " ") %>% 
  petersenlab::cleanUpNames(.)

nfl_contractYearQBR_weekly <- nfl_playerContractYears %>% 
  dplyr::filter(position == "QB") %>% 
  dplyr::full_join(
    .,
    nfl_espnQBR_weekly,
    by = c("nameMerge","team","season")
  )

@@

nfl_contractYearQBRsubset_weekly <- nfl_contractYearQBR_weekly %>% 
  dplyr::filter(season_type == "Regular") %>% 
  dplyr::arrange(nameMerge, season, season_type, game_week) %>% 
  mutate(
    player = coalesce(player, name_display),
    position = "QB") %>% 
  group_by(nameMerge, player_id) %>% 
  fill(player, .direction = "downup")

# Merge with age and experience
nfl_contractYearQBRsubset_weekly <- player_statsContractsSubset_offense_weekly %>% 
  dplyr::filter(position == "QB") %>% 
  dplyr::select(nameMerge, season, week, age, years_of_experience) %>% 
  full_join(
    nfl_contractYearQBRsubset_weekly,
    by = c("nameMerge","season", c("week" = "game_week"))
  ) %>% select(player_id, season, week, player, everything()) %>% 
  arrange(player_id, season, week)

@@

nfl_contractYearQBR_seasonal[sapply(nfl_contractYearQBR_seasonal, is.infinite)] <- NA
